### 2015-09-01 swmpr_manu.tex
created plos reject branch for future ref

% Remove comment for double spacing
\usepackage{setspace} 
\doublespacing

@@

\begin{knitrout}\small
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
> # import all paramaters for the station
> # three most recent records
> exdat <- all_params('apadbwq', Max = 3, trace = F)
> exdat
##         datetimestamp temp f_temp spcond f_spcond sal f_sal do_pct
## 1 2015-04-21 13:00:00   21      0   0.07        0   0     0     99
## 2 2015-04-21 13:15:00   21      0   0.05        0   0     0     99
## 3 2015-04-21 13:30:00   22      0   0.03        0   0     0     98
##   f_do_pct do_mgl f_do_mgl depth f_depth ph f_ph turb f_turb chlfluor
## 1        0      9        0  0.02       0  8    0    2      0       NA
## 2        0      9        0  0.02       0  8    0    2      0       NA
## 3        0      8        0  0.02       0  8    0   16      0       NA
##   f_chlfluor level f_level cdepth clevel f_cdepth f_clevel
## 1         -2    NA      -1  -0.01     NA        3         
## 2         -2    NA      -1   0.00     NA        3         
## 3         -2    NA      -1   0.00     NA        3
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

% Remove comment for double spacing
\usepackage{setspace} 
% \doublespacing

@@

\begin{knitrout}\small
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
> # import all paramaters for the station
> # three most recent records
> exdat <- all_params('apadbwq', Max = 3, trace = F)
> exdat
##         datetimestamp temp f_temp spcond f_spcond sal f_sal do_pct
## 1 2015-08-18 07:00:00   28      0     34        0  21     0     77
## 2 2015-08-18 07:15:00   28      0     34        0  21     0     75
## 3 2015-08-18 07:30:00   28      0     33        0  21     0     82
##   f_do_pct do_mgl f_do_mgl depth f_depth ph f_ph turb f_turb chlfluor
## 1        0      5        0     2       0  8    0   13      0       NA
## 2        0      5        0     2       0  8    0    9      0       NA
## 3        0      6        0     2       0  8    0   11      0       NA
##   f_chlfluor level f_level cdepth clevel f_cdepth f_clevel
## 1         -2    NA      -1     NA     NA       -1         
## 2         -2    NA      -1     NA     NA       -1         
## 3         -2    NA      -1     NA     NA       -1
\end{verbatim}
\end{kframe}
\end{knitrout}
